---
title: "lab 10!!!!!!!!!!!!!!wtf!!!!"
author: "Shayan Kaveh"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# that which is new
library(beepr)
library(paletteer)
library(praise)
library(sf)
library(cowsay)

# that which we know
library(tidyverse) #duh
library(usethis)
library(janitor)
```

## beepr beep beep doodoo

Use the function `beep()` in the beepr package to make an audio alert when your code is done running. I like `beep(8)` ... good beep.

```{r, eval = FALSE}
for (i in rev(seq(1:99))) {
  
  print(paste(i, "bottles of beer on the wall"))
}

beep(4) # this makes an audio alert for when it's done
```

## praise and cowsay

Packages built with a single purpose: to be kind and fun.

```{r}
praise("${Exclamation}, ${EXCLAMATION}... ${exclamation}!!!!")

praise("Holy ${exclamation}, Batman - this code is ${ADJECTIVE}!")
```

Use cowsay::say() to make a character say something to you

Use `usethis::edit_r_profile()` to get to r profile and edit this

Use `usethis::use_git()` in the console to commit a file to Git after starting the document already not on version control

Use `usethis::use_github()` to create a repo
